---
title: "Introduction to CountReg"
author: "Christoph Kiefer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CountReg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# First steps
In this article, I will mainly focus on introducing the main function `countreg()`. The other functions available in this package are helper functions for `countreg()`. However, you might take a look at the documentation of the `example01` dataset, which we will use throughout this article to fit some count regression models. 

```{r setup}
library(CountReg)
```
After loading the library, we can use `example01`, a dataset from the ACTIVE cognitive trial. The variables are:

* Dependent variable `dv`: count of correctly answered items
* Treatment variable `treat`: with values `treat=0` for control and `treat=2` for treatment
* Latent covariate *external locus of control* measured by
    * indicator variable `z11`
    * indicator variable `z12`
* Latent covariate *internal locus of control* measured by
    * indicator variable `z21`
    * indicator variable `z22`
* Latent covariate *depression* measured by
    * indicator variable `z41`
    * indicator variable `z42`
    * indicator variable `z43`
    
# 1. Scenario: Intercept-only in a single group
This scenario could also be named *mean of dv*, because that is exactly, what `countreg()` will return. Its a good start, to explain the arguments that `countreg()` accepts. We have to specify a formula, which is `forml='dv ~ 1'`, a dataset (which is `data=example01`), and a family, which is a character variable `family = 'poisson'` (taking `poisson` or `nbinom` as arguments). The arguments `lv` and `group` are for latent covariates and multi-group analysis.

```{r}
fit <- countreg(forml = 'dv ~ 1', lv = NULL, group = NULL, data = example01, family = "poisson")
summary(fit)
```
The `summary` function provides parameter estimates and standard error for the specified model.
    
    